Trends of downward SDR in Thessaloniki

### 2023-05-05 Article.Rmd
Commit 2023-05-05 19:17

output:  
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        yes
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5
  html_document:
    toc:             true
    fig_width:       7.5
    fig_height:      5

>>>>

output:  
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        no
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5
  html_document:
    toc:             true
    fig_width:       7.5
    fig_height:      5
